Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-05-30 draft/accordionComplexSurfaces.tex
Definition of the bound quiver of a dissection.

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, overpic, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
%\usepackage[bottom]{footmisc}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual cellular dissections~$\dissection$ and~$\dissection\dual$.
Let~$I$ denote the interior points and $B$ the blossom points.

\begin{definition}
\label{def:quiverDualDissections}
The bound quiver of a dissection~$\dissection$ is defined rotating around each face of~$\dissection$. Define also the blossoming quiver of~$\dissection$. Note that boundary edges of~$\dissection$ get two blossoms.
\end{definition}

>>>>

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
%\usepackage[bottom]{footmisc}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

Let~$\dissection$ and~$\dissection\dual$ be two dual cellular dissections of a marked surface~$(\surface, V\sqcup V\dual)$.
Let $B$ be the set of blossom points.

\begin{definition}
\label{def:quiverDualDissections}
The bound quiver of the dissection~$\dissection$ is the bound quiver $\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ defined as follows:
\begin{itemize}
 \item the set of vertices of~$Q_{\dissection}$ is the set or edges of $\dissection$;
 \item there is an arrow from~$a$ to~$b$ for each common endpoint~$v$ of~$a$ and~$b$ such that~$b$ comes immediately after~$a$ in the clockwise order around~$v$;
 \item the ideal~$I_{\dissection}$ is generated by the paths of length two in~$Q_{\dissection}$ obtained by composing arrows which correspond to triples of consecutive edges in a face of~$\dissection$.
\end{itemize}
The bound quiver of the dissection~$\dissection\dual$ is the bound quiver $\bar Q_{\dissection\dual} = (Q_{\dissection\dual}, I_{\dissection\dual})$ defined by replacing~$\dissection$ by~$\dissection\dual$ in the above.
\end{definition}

It is not hard to see that~$\bar Q_{\dissection} = (Q_{\dissection}, I_{\dissection})$ is a gentle bound quiver,
and that the vertices corresponding to boundary edges of~$\dissection$ are blossoming vertices.
\pierreguy{Be more precise on the ``are blossiming vertices'' part of this sentence.}
